Methods for Large Scale Learning to Rank

### 2014-04-04 report/Chapters/CrossBenchmarkComparison.tex
ndcg10 verwerkt in tabel

\section{Evaluation Results Found in Literature}
\begin{table}[!h]
\begin{tabular}{l|l|l}
AdaRank-\acs{MAP} & \acs{GP}Rank & RankAgg\ac{nDCG} \\ 
AdaRank-\acs{nDCG} & GRank\acs{RLS} & RankBoost \\ 
ADMM & Group\acs{CE} \cite{Lin2011} & RankCSA \cite{He2010} \\ 
Approx\acs{AP} \cite{Qin2010b} & Group\acs{MLE} & RankDE \\ 
Approx\acs{nDCG} \cite{Qin2010b} & IntervalRank \cite{Moon2010} & RankELM (pairwise) \\ 
BagBoo & \acs{IP}Rank & RankELM (pointwise) \\ 
Best Single Feature & KeepRank & Ranking Committee Perceptron \cite{Elsas2008} \\ 
BL-MART \cite{Ganjisaffar2011c} & Kernel-\acs{PCA} & RankMGP \\ 
BoltzRank-Single \cite{Volkovs2009} & KL-\acs{CRF} & RankNet \\ 
BoltzRank-Pair \cite{Volkovs2009} & LAC-MR-OR \cite{Veloso2008} & Rank\ac{RLS} \\ 
BT \cite{Zhou2008} & LambdaMART & Rank\ac{SVM} \\ 
C-\acs{CRF} \cite{Qin2008b} & LambdaNeuralRank \cite{Papini2012} & Rank\ac{SVM}-Primal \\ 
\acs{CA} & LambdaRank & Rank\acs{SVM}-Struct \\ 
\ac{CC}Rank & LARF & RE-QR \\ 
CoList & Linear Regression & REG-SHF-SDCG \\ 
Consistent-RankCosine & List\acs{MLE} & Regression \\ 
DCMP \cite{Renjifo2012} & ListNet & Ridge Regression \\ 
DirectRank & ListReg & RSRank \\ 
Energy\ac{nDCG} \cite{Freno2011} & LRUF & SmoothGrad \\ 
FBPCRank \cite{Lai2011} & MBP & SmoothRank \\ 
FenchelRank \cite{Lai2013} & MHR & SoftRank \\ 
FocusedBoost \cite{Niu2012} & MultiStageBoost & SortNet \cite{Rigutini2008} \\ 
FocusedNet \cite{Niu2012} & NewLoss & SparseRank \\ 
Focused\ac{SVM} \cite{Niu2012} & OWPC & \acs{SVD}-RankBoost \cite{Lin2009} \\ 
FPRank & PERF-\ac{MAP} & \ac{SVM}$^{\ac{MAP}}$ \\ 
FRank & PermuRank \cite{Xu2008} & SwarmRank \\ 
FSMRank & Q.D.\acs{KNN} & TGRank \\ 
FSM$^{\acs{MAP}}$ & RandomForest & TM \cite{Zhou2008} \\ 
GAS-E & Rank-PMBGP \cite{Sato2013} & VFLR \\ 
\end{tabular}
\caption{Learning-to-Rank algorithms with measurements on benchmark datasets}
\label{ltr_methods_used}
\end{table}

>>>>

\section{Evaluation Results Found in Literature}
\begin{table}[!h]
\scalebox{0.85}{
\begin{tabular}{|l|l|l||l|l|l|}
Method & Described & Evaluated & Method & Described & Evaluated \\
\hline 
AdaRank-\acs{MAP} &  &  & Linear Regression &  & \cite{Wang2012} \\ 
AdaRank-\acs{nDCG} &  & \cite{Busa-Fekete2013,Tan2013} & List\acs{MLE} &  & \cite{Lin2010, Gao2014} \\ 
ADMM & \cite{Duh2011} & \cite{Duh2011} & ListNet &  &  \\ 
Approx\acs{AP} & \cite{Qin2010b} & \cite{Qin2010b} & ListReg & \cite{Wu2011} & \cite{Wu2011} \\ 
Approx\acs{nDCG} & \cite{Qin2010b} & \cite{Qin2010b} & LRUF & \cite{Torkestani2012b} & \cite{Torkestani2012b} \\ 
BagBoo &  &  & MCP & \cite{Laporte2013} & \cite{Laporte2013} \\ 
Best Single Feature &  & \cite{Gomes2013} & MHR &  &  \\ 
BL-MART & \cite{Ganjisaffar2011c} & \cite{Ganjisaffar2011c} & MultiStageBoost & \cite{Kao2013} & \cite{Kao2013} \\ 
BoltzRank-Single & \cite{Volkovs2009} & \cite{Volkovs2009} & NewLoss & \cite{Peng2010} & \cite{Peng2010} \\ 
BoltzRank-Pair & \cite{Volkovs2009} & \cite{Volkovs2009} & OWPC & \cite{Usunier2009} & \cite{Usunier2009} \\ 
BT & \cite{Zhou2008} & \cite{Zhou2008} & PERF-\acs{MAP} &  & \cite{Torkestani2012b} \\ 
C-\acs{CRF} & \cite{Qin2008b} & \cite{Qin2008b} & PermuRank & \cite{Xu2008} & \cite{Xu2008} \\ 
CA &  & \cite{Busa-Fekete2013,Tan2013} & Q.D.\acs{KNN} &  &  \\ 
CCRank &  &  & RandomForest &  & \cite{Gomes2013} \\ 
CoList & \cite{Gao2014} & \cite{Gao2014} & Rank-PMBGP & \cite{Sato2013} & \cite{Sato2013} \\ 
Consistent-RankCosine &  & \cite{Tan2013} & RankAgg\acs{nDCG} &  &  \\ 
DCMP & \cite{Renjifo2012}  & \cite{Renjifo2012}  & RankBoost &  & \cite{Busa-Fekete2013} \\ 
DirectRank & \cite{Tan2013} & \cite{Tan2013} & RankCSA & \cite{He2010} & \cite{He2010} \\ 
Energy\acs{nDCG} & \cite{Freno2011} & \cite{Freno2011} & RankDE &  & \cite{Sato2013} \\ 
FBPCRank & \cite{Lai2011} & \cite{Lai2011} & RankELM (pairwise) & \cite{Zong2013} & \cite{Zong2013} \\ 
FenchelRank & \cite{Lai2013} & \cite{Lai2013, Lai2013b,Laporte2013} & RankELM (pointwise) & \cite{Zong2013} & \cite{Zong2013} \\ 
FocusedBoost & \cite{Niu2012} & \cite{Niu2012} & RankMGP & \cite{Lin2012} & \cite{Lin2012} \\ 
FocusedNet & \cite{Niu2012} & \cite{Niu2012} & RankNet &  & \cite{Busa-Fekete2013, Papini2012, Niu2012} \\ 
Focused\acs{SVM} & \cite{Niu2012} & \cite{Niu2012} & Rank\acs{RLS} &  &  \\ 
FP-Rank & \cite{Song2013} & \cite{Song2013} & Rank\acs{SVM} &  & \cite{Busa-Fekete2013, Freno2011} \\ 
FRank &  & \cite{Wang2012} & Rank\acs{SVM}-Primal &  &  \\ 
FSMRank & \cite{Lai2013c} & \cite{Lai2013c,Laporte2013} & Rank\acs{SVM}-Struct &  &  \\
FSM$^{\acs{SVM}}$ & & \cite{Lai2013c} & RCP & \cite{Elsas2008} & \cite{Elsas2008} \\ 
GAS-E &  & \cite{Lai2013c} & RE-QR & \cite{Veloso2010} & \cite{Veloso2010} \\ 
\acs{GP}Rank &  & \cite{Torkestani2012} & REG-SHF-SDCG & \cite{Wu2009} & \cite{Wu2009} \\ 
GRank\acs{RLS} & \cite{Pahikkala2010} & \cite{Pahikkala2010} & Ridge Regression &  &  \\ 
Group\acs{CE} & \cite{Lin2011} & \cite{Lin2011} & RSRank &  &  \\ 
Group\acs{MLE} &  &  & SmoothGrad &  & \cite{Tan2013} \\ 
IntervalRank & \cite{Moon2010} & \cite{Moon2010} & SmoothRank & \cite{Chapelle2010} & \cite{Chapelle2010} \\ 
\acs{IP}Rank &  & \cite{Torkestani2012} & SoftRank &  & \cite{Qin2010b} \\ 
KeepRank & \cite{Chen2009} & \cite{Chen2009} & SortNet & \cite{Rigutini2008} & \cite{Rigutini2008,Freno2011} \\ 
Kernel-\acs{PCA} &  &  & SparseRank & \cite{Lai2013b} & \cite{Lai2013b} \\ 
KL-\acs{CRF} & \cite{Volkovs2011} &  & \acs{SVD}-RankBoost & \cite{Lin2009} & \cite{Lin2009} \\ 
LAC-MR-OR & \cite{Veloso2008} & \cite{Veloso2008} & \acs{SVM}$^{\acs{MAP}}$ &  & \cite{Wang2012} \\ 
LambdaMART & \cite{Burges2010} & \cite{Asadi2013a} & SwarmRank &  & \cite{Sato2013} \\ 
LambdaNeuralRank & \cite{Papini2012} & \cite{Papini2012} & TGRank &  &  \\ 
LambdaRank &  &  & TM & \cite{Zhou2008} & \cite{Zhou2008, Papini2012,Tan2013} \\ 
LARF & \cite{Torkestani2012} & \cite{Torkestani2012} & VFLR & \cite{Cai2012} & \cite{Cai2012} \\ 
\end{tabular}}
\caption{Learning-to-Rank algorithms with measurements on benchmark datasets}
\label{ltr_methods_used}
\end{table}
